---
title: "Data607_Web_API"
author: "Mahmud Hasan Al Raji"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction: The New York Times web site provides a rich set of APIs (link: https://developer.nytimes.com/apis). For this assignment, my task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame. Here, I chose the movie critics JSON data for all reviewer from New York Times Movie Review APIs.


# Loading libraries 
```{r }
library(jsonlite)
library(httr)
library(ggplot2)
library(dplyr)

```

# Constructing an interface with required API and checking the response 
```{r }
# link to the API output as a JSON file
url_json <- "https://api.nytimes.com/svc/movies/v2/critics/all.json?api-key=VAhjWqxLrMQTPsvIOYxaH7gFuKWE79en"
#get the raw json into R
resp <- GET(url_json)
resp
```

# Reading movie critics JSON data and converting it into a R dataframe
```{r }
critics_data<- fromJSON(rawToChar(resp$content))%>% data.frame
glimpse(critics_data)
```

# Data tidying and subsetting 
```{r }
#Renaming two columns
critics_data<-rename(critics_data,critic_name=results.display_name,critic_status=results.status)
#Sub setting data frame with new column names
critics_data1<-select(critics_data,critic_name,critic_status)
head(critics_data1)
#Replace empty value with NA in critic_status column
critics_data1$critic_status[critics_data1$critic_status==''] <- NA
head(critics_data1)
#Finding critics status count data
critics_status_count_data <- critics_data1 %>% count(critic_status)
critics_status_count_data
```

# Plotting critics status based on their occuring number
```{r}
ggplot(data=critics_status_count_data, aes(x=critic_status, y=n)) +
  geom_bar(stat="identity") + 
    labs(
      x = "Critic Status",
      y = "Number of Critic Status",
      title = "The number of critic status"
    ) + 
    coord_flip()
```

# Conclusion: In this assignment, I chose movie critics data for all reviewer from New York Times Movie Review API.I collected JSON data through a API connection and transformed that JSON data into a R data frame. Finally, I plotted a bar graph to see the critics status based on their occuring numbers.

